### 2014-10-22 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Edits to captions and figure labels throughout

\begin{figure}[!ht]
\includegraphics[width=5.0in]{../Figures/Plan_Second_Floor}
\includegraphics[width=5.0in]{../Figures/Plan_First_Floor}
\includegraphics[width=5.0in]{../Figures/Plan_Basement_Floor}
\caption[Plan view of second floor, first floor, and basement floor of structure.]
{Plan view of second floor (top), first floor (middle), and basement floor (bottom) of structure. The fire originated in the living room on the basement floor. Stairs and rooms are identified using information collected by NIST. The sub-basement level was not connected to the other three levels of the house and is not shown.}
\label{fig:floor_plan}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=5.50in]{../Figures/Post_Exterior_Front} \\
\vspace{0.1in}
\includegraphics[width=3.50in]{../Figures/Post_Exterior_Rear}
\caption[Front and rear exterior of the structure after the incident.]
{Front (top) and rear (bottom) exterior sides of the structure after the incident. Photographs courtesy of the San Francisco Fire Department.}
\label{fig:post_exterior}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=5.0in]{../Figures/SMV_Exterior_Grid_Front} \\
\includegraphics[width=4.5in]{../Figures/SMV_Exterior_Grid_Rear}
\caption[Front and rear of the structure with a 10~cm computational mesh.]
{Front (top) and rear (bottom) sides of the structure with a 10~cm computational mesh.}
\label{fig:SMV_exterior_grid}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=5.5in]{../Figures/Fire_HRR_w_FDS}
\caption[Predicted HRR vs. time from the FDS simulation.]
{Comparison of prescribed and predicted HRRs from the FDS simulation. The vertical line indicates the time at which the rear basement windows began to fail (342~s).}
\label{fig:hrr_w_fds}
\end{figure}

@@

Figure~\ref{fig:timeline_comparison_rear} shows a time series comparison of on-scene photographs and Smokeview snapshots of flaming combustion that occurred through the failed windows on the rear side of the structure. In this figure, the first photograph is shown at a simulation time of 321~s (approximately 20~s before the first rear basement window failed), the second photograph is shown at a simulation time of 349~s (approximately 10~s after the first rear basement window failed), the third photograph is shown at a simulation time of 440~s (approximately when the third rear basement window failed), and the fourth photograph is shown at a simulation time of 450~s (approximately when all of the rear basement windows had failed). Figure~\ref{fig:timeline_comparison_front} shows a comparison of an on-scene photograph and Smokeview snapshot of smoke coming out of the front side of the structure at approximately the time when the rear windows began to fail.

@@

\begin{figure}[!ht]
\includegraphics[width=5.0in]{../Figures/Photo_Front_350_s}
\includegraphics[width=5.0in]{../Figures/SMV_Front_350_s}
\caption[Snapshot of smoke coming out of the front side of the structure.]
{Comparison of an on-scene photograph and Smokeview snapshot of smoke coming out of the front side of the structure. The on-scene time is indicated on the photograph (top), and the corresponding simulation time is indicated on the Smokeview snapshot (bottom). For more information on the fire incident and simulation timeline, refer to Table~\ref{tab:combined_timeline}. Photograph courtesy of the San Francisco Fire Department.}
\label{fig:timeline_comparison_front}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=4.5in]{../Figures/SMV_Vel_340_s}
\input{../Figures/colorbar_metric_velo}
\input{../Figures/colorbar_std_velo}
\includegraphics[width=4.5in]{../Figures/SMV_Vel_402_s}
\input{../Figures/colorbar_metric_velo}
\input{../Figures/colorbar_std_velo}
\caption[Simulated velocity contours on the right interior side of the structure.]
{Simulated velocity contours on the right interior side of the structure, 2~s before (top) and 60~s after (bottom) the first rear basement window failure.}
\label{fig:smv_velocity}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=4.5in]{../Figures/SMV_Vel_Vec_340_s}
\input{../Figures/colorbar_metric_velo}
\input{../Figures/colorbar_std_velo}
\includegraphics[width=4.5in]{../Figures/SMV_Vel_Vec_402_s}
\input{../Figures/colorbar_metric_velo}
\input{../Figures/colorbar_std_velo}
\caption[Simulated velocity vectors on the right interior side of the structure.]
{Simulated velocity vectors on the right interior side of the structure, 2~s before (top) and 60~s after (bottom) the first rear basement window failure.}
\label{fig:smv_velocity_vectors}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=4.3in]{../Figures/SMV_Temp_340_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\includegraphics[width=4.3in]{../Figures/SMV_Temp_402_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\caption[Simulated temperature contours on the right interior side of the structure.]
{Simulated temperature contours on the right interior side of the structure, 2~s before (top) and 60~s after (bottom) the first rear basement window failure.}
\label{fig:smv_temperature}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=4.3in]{../Figures/SMV_Temp_Vec_340_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\includegraphics[width=4.3in]{../Figures/SMV_Temp_Vec_402_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\caption[Simulated temperature vectors on the right interior side of the structure.]
{Simulated temperature vectors on the right interior side of the structure, 2~s before (top) and 60~s after (bottom) the first rear basement window failure.}
\label{fig:smv_temperature_vectors}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=4.3in]{../Figures/SMV_Top_Temp_340_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\caption[Simulated temperature contours on the first floor before basement window failure.]
{Top view of simulated temperature contours on the first floor, 0.3~m (1~ft) above the floor, 2~s before the first rear basement window failure. The orange markers indicate the locations of the downed firefighters.}
\label{fig:smv_flow_path_top_1}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=4.3in]{../Figures/SMV_Top_Temp_402_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\includegraphics[width=4.3in]{../Figures/SMV_Top_Temp_462_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\caption[Simulated temperature contours on the first floor after basement window failure.]
{Top view of simulated temperature contours on the first floor, 0.3~m (1~ft) above the floor, 60~s (top) and 120~s (bottom) after the first rear basement window failure.}
\label{fig:smv_flow_path_top_2}
\end{figure}

>>>>

\begin{figure}[!ht]
\includegraphics[width=5.0in]{../Figures/Plan_Second_Floor}
\includegraphics[width=5.0in]{../Figures/Plan_First_Floor}
\includegraphics[width=5.0in]{../Figures/Plan_Basement_Floor}
\caption[Plan view of the second floor, first floor, and basement floor.]
{Plan view of the second floor (top), first floor (middle), and basement floor (bottom). The fire originated in the living room on the basement floor. Stairs and rooms are identified using information collected by NIST. The sub-basement level was not connected to the other three levels of the house and is not shown.}
\label{fig:floor_plan}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=5.50in]{../Figures/Post_Exterior_Front} \\
\vspace{0.1in}
\includegraphics[width=3.50in]{../Figures/Post_Exterior_Rear}
\caption[Front and rear sides of the structure after the incident.]
{Front side (top) and rear side (bottom) of the structure after the incident. Photographs courtesy of the San Francisco Fire Department.}
\label{fig:post_exterior}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=5.0in]{../Figures/SMV_Exterior_Grid_Front} \\
\includegraphics[width=4.5in]{../Figures/SMV_Exterior_Grid_Rear}
\caption[Front and rear sides of the structure with a 10~cm computational mesh.]
{Front side (top) and rear side (bottom) of structure with a 10~cm computational mesh.}
\label{fig:SMV_exterior_grid}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=5.5in]{../Figures/Fire_HRR_w_FDS}
\caption[Predicted HRR vs. time from the simulation.]
{Comparison of prescribed and predicted HRRs from the simulation. The vertical line indicates the time at which the rear basement windows began to fail (342~s).}
\label{fig:hrr_w_fds}
\end{figure}

@@

Figure~\ref{fig:timeline_comparison_rear} shows a time series comparison of on-scene photographs and Smokeview snapshots of flaming combustion that occurred through the failed windows on the rear side of the structure. In this figure, the first photograph is shown at a simulation time of 321~s (approximately 20~s before the first rear basement window failed), the second photograph is shown at a simulation time of 349~s (approximately 10~s after the first rear basement window failed), the third photograph is shown at a simulation time of 440~s (approximately when the third rear basement window failed), and the fourth photograph is shown at a simulation time of 450~s (approximately when all of the rear basement windows had failed). Figure~\ref{fig:timeline_comparison_front} shows a comparison of an on-scene photograph and Smokeview snapshot of smoke flowing out of the front side of the structure at approximately the time when the rear windows began to fail.

@@

\begin{figure}[!ht]
\includegraphics[width=5.0in]{../Figures/Photo_Front_350_s}
\includegraphics[width=5.0in]{../Figures/SMV_Front_350_s}
\caption[Snapshot of smoke flowing out of the doors on the front side of the structure.]
{Comparison of an on-scene photograph and Smokeview snapshot of smoke flowing out of the doors on the front side of the structure. The on-scene time is indicated on the photograph (top), and the corresponding simulation time is indicated on the Smokeview snapshot (bottom). For more information on the fire incident and simulation timeline, refer to Table~\ref{tab:combined_timeline}. Photograph courtesy of the San Francisco Fire Department.}
\label{fig:timeline_comparison_front}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=4.5in]{../Figures/SMV_Vel_340_s}
\input{../Figures/colorbar_metric_velo}
\input{../Figures/colorbar_std_velo}
\includegraphics[width=4.5in]{../Figures/SMV_Vel_402_s}
\input{../Figures/colorbar_metric_velo}
\input{../Figures/colorbar_std_velo}
\caption[Simulated velocity contours on the right interior side of the structure.]
{Simulated velocity contours on the right interior side of the structure, 2~s before (top) and 60~s after (bottom) the first rear basement window failure. The structure and compartment labels are shown in Fig.~\ref{fig:smv_pressure}.}
\label{fig:smv_velocity}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=4.5in]{../Figures/SMV_Vel_Vec_340_s}
\input{../Figures/colorbar_metric_velo}
\input{../Figures/colorbar_std_velo}
\includegraphics[width=4.5in]{../Figures/SMV_Vel_Vec_402_s}
\input{../Figures/colorbar_metric_velo}
\input{../Figures/colorbar_std_velo}
\caption[Simulated velocity vectors on the right interior side of the structure.]
{Simulated velocity vectors on the right interior side of the structure, 2~s before (top) and 60~s after (bottom) the first rear basement window failure. The structure and compartment labels are shown in Fig.~\ref{fig:smv_pressure}.}
\label{fig:smv_velocity_vectors}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=4.3in]{../Figures/SMV_Temp_340_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\includegraphics[width=4.3in]{../Figures/SMV_Temp_402_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\caption[Simulated temperature contours on the right interior side of the structure.]
{Simulated temperature contours on the right interior side of the structure, 2~s before (top) and 60~s after (bottom) the first rear basement window failure. The structure and compartment labels are shown in Fig.~\ref{fig:smv_pressure}.}
\label{fig:smv_temperature}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=4.3in]{../Figures/SMV_Temp_Vec_340_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\includegraphics[width=4.3in]{../Figures/SMV_Temp_Vec_402_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\caption[Simulated temperature vectors on the right interior side of the structure.]
{Simulated temperature vectors on the right interior side of the structure, 2~s before (top) and 60~s after (bottom) the first rear basement window failure. The structure and compartment labels are shown in Fig.~\ref{fig:smv_pressure}.}
\label{fig:smv_temperature_vectors}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=4.3in]{../Figures/SMV_Top_Temp_340_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\caption[Simulated temperature contours on the first floor before basement window failure.]
{Top view of simulated temperature contours on the first floor, 0.3~m (1~ft) above the floor, 2~s before the first rear basement window failure. The square markers indicate the locations of the downed firefighters.}
\label{fig:smv_flow_path_top_1}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=4.3in]{../Figures/SMV_Top_Temp_402_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\includegraphics[width=4.3in]{../Figures/SMV_Top_Temp_462_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\caption[Simulated temperature contours on the first floor after basement window failure.]
{Top view of simulated temperature contours on the first floor, 0.3~m (1~ft) above the floor, 60~s after (top) and 120~s after (bottom) the first rear basement window failure.}
\label{fig:smv_flow_path_top_2}
\end{figure}
